%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
%

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
%


%\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
%\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}


\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	Name And Address Section
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf David Devecsery} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{University of Michigan - Ann Arbor} % Your address
\moveleft.5\hoffset\centerline{4929 BBB, 2260 Hayward St} % Your address
\moveleft.5\hoffset\centerline{Ann Arbor, MI 48109}
\moveleft.5\hoffset\centerline{ddevec@umich.edu}
\moveleft.5\hoffset\centerline{http://www.umich.edu/\textasciitilde{}ddevec}

%----------------------------------------------------------------------------------------

\begin{resume}
 

\section{Education}

{\sl PhD.} \\
University of Michigan, Ann Arbor, MI, April, 2018 \\
Concentration: Computer Science Engineering \\
Advisor: Peter M. Chen

{\sl Masters of Science,} Engineering \\
University of Michigan, Ann Arbor, MI, April 2013 \\
Concentration: Computer Science Engineering

{\sl Bachelor of Science,} Engineering \\
University of Michigan, Ann Arbor, MI, April 2011 \\
Concentration: Computer Engineering

\section{Appointments}

{\sl Assistant Professor} \\
Georgia Institute of Technology, Atlanta, GA, 2018-Present \\
School of Computer Science

\section{Research \\Area}
Software system errors and misbehaviors present a major problem in
writing, maintaining, and using significant software bases.  Security
vulnerabilities can lead to catastrophic data and privacy losses and
great fiscal cost.  Software downtime due to bugs is highly costly for
companies, even when software doesn't crash the cost of developer
effort to eliminate bugs is far too high.  My research seeks to
greatly reduce the burden of software errors.  In an ideal world, once
an individual learns of some mis-behavior, such as a security
vulnerability, information leak, mis-configuration, erroneous data, or
unexpected crash; he or she should have tools which quickly identify
and understand the origin of the error, what state it has affected,
and the system should either identify a solution to the problem, or
self correct.

\section{Research Projects}
\textbf{Optimistic Hybrid Analysis} -- A novel method of dramatically
accelerating dynamic analysis, which combines speculation, a novel
static analysis called predicated static analysis, and speculative
dynamic analysis to ultimately produce a dynamic analysis which is far
more efficient than a traditional dynamic analysis, but just as
accurate.

\textbf{Eidetic Systems} -- A computer operating system which uses
novel deterministic record/replay technology to by default remember
and enable powerful lineage queries for all computation (process
memory states, and inter-process communication).

%\item
\textbf{Parallel Analysis} -- I've used record/replay technology and
epoch parallelism to efficiently parallelize traditionally
heavy-weight difficult to parallelize analyses.  Methods show
super-linear scaling for race-detection, and can scale taint tracking
to 100's of CPU cores.

%  I've worked on parallelizing
%  \emph{Data Race Detection} and \emph{Dynamic Information Flow
%  Tracking}.
%\end{itemize}

%Broadly, my research focus is on Operating Systems.  More specifically
%my research focuses on improving the reliability of programs through
%system-level abstractions.  My most recent work is about ``Eidetic
%Systems," or systems which store their entire computation history.
%``Eidetic Systems" can analyze any computation done on them, to
%understand how past computations have effected current states.

\section{Non-Research \\ Projects}
\textbf{TalkingBook} -- A computer system catered to the challenges of
the developing world, specifically targeting extremely low-cost and
power consumption.  We have developed a custom microprocessor with
novel memory architecture and operating system designed to be
accessible to the world's poorest people.  A joint work between the
University of Michigan and Literacy Bridge
(http://literacybridge.org).

\section{Publications}
\textbf{Peer-Reviewed Publications}\\
Subarno Banerjee, David Devecsery, Peter Chen, Satish Narayanasamy
``Iodine: Fast Dynamic Taint Tracking Using Rollback-free Optimistic
Hybrid Analysis'', {\sl To appear Proceedings of the 28th USENIX
Security Symposium} (Oakland), August 2019.

David Devecsery, Peter Chen, Satish Narayanasamy, Jason Flinn, ``Fast,
Sound Dynamic Analysis through Predicated Static Analysis and
Speculative Execution'', {\sl ACM International Conference
on Architectural Support for Programming Languages and Operating
Systems} (ASPLOS), March 2018.

Andrew Quinn, David Devecsery, Peter M. Chen, and Jason Flinn,
``JetStream: Cluster-Scale Parallelization of Information Flow
Queries'', {\sl Proceedings of the 12th USENIX Symposium on Operating
Systems Design and Implementation} (OSDI), November 2016.

David Devecsery, Michael Chow, Xianzheng Dou, Peter M Chen, Jason
Flinn, ``Eidetic Systems'' {\sl Proceedings of the 2014 conference on
Operating System Design and Implementation} (OSDI), October 2014.

Benjamin Wester, David Devecsery, Peter M. Chen, Jason Flinn, Satish
Narayanasamy, ``Parallelizing Data Race Detection'', {\sl Proceedings
of the 2013 International Conference on Architectural Support for
Programming Languages and Operating Systems} (ASPLOS), March 2013.

Foo, Z.; Devecsery, D.; Ghaed, M.; Lee, I.; Madhavan, A.; Park, Y.;
Rao, A.; Renner, Z.; Roberts, N.; Schulman, A.; Vinay, V.; Wieckowski,
M.; Yoon, D.; Schmidt, C.; Schmid, T.; Dutta, P.; Chen, P.; Blaauw,
D.; , ``A low-cost audio computer for information dissemination among
illiterate people groups,'' {\sl Custom Integrated Circuits Conference}
(CICC), 2012 IEEE , vol., no., pp.1-4, 9-12 Sept. 2012

%Huey-Ming Tzeng, Atul Prakash, Mark Brehob, Allison Anderson, David
%Andrew Devecsery and Chang-Yi Yin, ``How Feasible Was a Bed-Height
%Alert System?”, {\sl Clinical Nursing Research} (SCI, SSCI) 2012
%
%Huey-Ming Tzeng, Atul Prakash, Mark Brehob, Allison Anderson, David
%Andrew Devecsery and Chang-Yi Yin, ``Keeping patient beds in a low
%position: an exploratory descriptive study to continuously monitor the
%height of patient beds in an adult acute surgical inpatient care
%setting," {\sl Contemporary Nursing} June 2012.

Zhiyoong Foo, David Devecsery, Thomas Schmid, N. Clark, Rebecca Frank,
M. Ghaed, Y. Kuo, In Hee Lee, Youn Sung Park, Zachary Renner,
Nathaniel Slottow, Vikas Vinay, Michael Wieckowski, Dongmin Yoon,
David Blaauw, Peter M. Chen, Prabal Dutta, Cliff Schmidt, ``A Case for
Custom Silicon in Enabling Low-Cost Information Technology for
Developing Regions'' , {\sl Proceedings of the 2010 Symposium on
Computing for Development} (SIGDEV) , December 2010.

\textbf{Presentations}\\
``Fast, Sound Dynamic Analysis through Predicated Static Analysis and
Speculative Execution'', David Devecsery, Peter Chen, Satish
Narayanasamy, Jason Flinn, {\sl ACM International Conference
on Architectural Support for Programming Languages and Operating
Systems} (ASPLOS), March 2018.

``Optimistic Hybrid Analysis'' David Devecsery, Peter Chen, Satish
Narayanasamy, Jason Flinn, {\sl Midwest PL Summit}, December 2016.

``Eidetic Systems'' David Devecsery, Michael Chow, Xianzheng Dou,
Peter M Chen, Jason Flinn, {\sl Proceedings of the 2014 conference
on Operating System Design and Implementation} (OSDI), October 2014.

``A Case for Custom Silicon in Enabling Low-Cost Information
Technology for Developing Regions'' Zhiyoong Foo, David Devecsery,
Thomas Schmid, N. Clark, Rebecca Frank, M. Ghaed, Y. Kuo, In Hee Lee,
Youn Sung Park, Zachary Renner, Nathaniel Slottow, Vikas Vinay,
Michael Wieckowski, Dongmin Yoon, David Blaauw, Peter M. Chen, Prabal
Dutta, Cliff Schmidt,  , {\sl Proceedings of the 2010 Symposium on
Computing for Development} (SIGDEV) , December 2010. (Presentation by
David Devecsery)

\textbf{Posters}\\
Andrew Quinn, David Devecsery, Peter M. Chen, and Jason Flinn,
``JetStream: Cluster-Scale Parallelization of Information Flow
Queries'' {\sl Proceedings of the 12th USENIX Symposium on Operating
Systems Design and Implementation} (OSDI), November 2016.

``Optimistic Static Analysis'' David Devecsery, Peter M Chen, Jason
Flinn, Satish Narayanasamy, {\sl The 24th ACM Symposium on Operating
Systems Principals} (SOSP), October 2015.

``Eidetic Systems'' David Devecsery, Michael Chow, Xianzheng Dou,
Peter M Chen, Jason Flinn, {\sl The 2014 conference
on Operating System Design and Implementation} (OSDI), October 2014.

``Flexible Replay Groups'' David Devecsery, Peter M Chen, Jason Flinn,
{\sl The 24th ACM Symposium on Operating Systems
Principals} (SOSP), November 2013.

\section{Teaching} \textbf{Georgia Tech} \\
Memory Models (CS8803) \hfill Fall 2018

\textbf{University of Michigan} \\
TA for Introduction to Operating Systems (EECS 482) \hfill Fall 2014 \\
TA for Computer Architecture (EECS 470) \hfill Winter 2011 \\

%
%\section{Representative \\ Course \\ Projects}
%\textbf{Advanced Security} \hfill Fall '12
%\begin{itemize}
%\item Designed a system to provide efficient unlimited watchpoints
%	using AMD's proposed transactional memory specification.
%\end{itemize}
%
%\textbf{Advanced Compilers} \hfill Winter '11
%\begin{itemize}
%\item Created an efficient Cache Profiler using Intel performance
%	counters, and Precise Event Based Sampling
%\end{itemize}
%
%\textbf{Advanced Operating Systems} \hfill Fall '11
%\begin{itemize}
%\item Tested transient failures of NAND Flash, and flash translation
%	layer vulnerabilities to these failures.
%\end{itemize}

\section{Service}
CSEG Board Game Night Organizer \hfill Winter 2013-Fall 2014 \\
Software Reading Group Organizer \hfill Winter 2012-Winter 2013 \\
Software Reading Group Volunteer Speaker \hfill Fall 2011-Present \\
Tutor in Computer Architecture and Operating Systems\hfill Fall 2011 \\
Mentor for TalkingBook Project \hfill Fall '12 - Present \\

\end{resume}
\end{document}
